---
title: "Reproducible Pitch"
author: "Harikrishna Vemula"
date: "1/19/2021"
output:
  slidy_presentation: default
  html_document:
    number_sections: yes
    toc: yes
  ioslides_presentation: default
mode: selfcontained
job: Reproducible Pitch Presentation
subtitle: MPG vs Variables
highlighter: highlight.js
widgets: bootstrap
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## ##

**Introduction**
This is Coursera's Week 4 Assignment of Developing Data Products course.
I have created a shiny web application using R Studio and deployed it in shiny server inorder to review by peers. 
I am also sharing the code in following github url for peers referance.

**Objective**

This shiny app demonstrating you how can we plot **mpg vs variables** from mtcars dataset.


## Analysis on mtcars Dataset

```{r}

library(datasets)
head(mtcars)

```

## Code

**UI CODE**

```{r echo=TRUE, warning=FALSE, message=FALSE, eval=FALSE}
library(shiny)

shinyUI(fluidPage(
  
  # Application title
  titlePanel("MPG Vs Variables"),
  
  sidebarPanel(
    
    selectInput("variable", "Variable:", 
                c("Number of cylinders" = "cyl",
                  "Number of forward gears" = "gear",
                  "Transmission" = "am",
                  "Gross horsepower" = "hp"))
  ),
  
  mainPanel(
    # Output: Formatted text for caption ----
    h3(textOutput("caption")),
    
    # Output: Plot of the requested variable against mpg ----
    plotOutput("mpgPlot")
  )
))
```

**SERVER CODE**
```{r echo=TRUE, warning=FALSE, message=FALSE, eval=FALSE}
library(shiny)
library(plotly)
mpgData <- mtcars
mpgData$am <- factor(mpgData$am, labels = c("Automatic", "Manual"))
shinyServer(function(input, output) {
  
  formulaText <- reactive({
    paste("miles per gallon vs ", input$variable)
  })
  
  output$caption <- renderText({
    formulaText()
  })
  output$mpgPlot <- renderPlot({
    ggplot(mpgData, aes_string(y=input$variable, x="mpg")) + geom_point()
  })
  
})
```

## Conclusion and Review

1) There are more **automatic** mpgs are with compare to **manual**
2) mpg values starts from **4** for cylinders where as **3** for gears


